Analyzing the impact of social attributes on the success of commit integration

### 2017-02-18 Paper/MSRChallenge2017.tex
added decision tree citations

We evaluated the predictive power of the social factors using a decision
tree.\todo{citation needed}
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the J48 Weka decision tree \todo{citation needed} with default settings. The 
decision trees were evaluated using ten fold cross validation with the data in
each data set.

@@

@@

@@

\noindent\textbf{Internal validity:}
One source of internal validity concern is the time mismatch between the
technical and social data.  We restricted the commits to only the commits in the
last three years of the data set to reduce this concern.
There is also a chance that scripts we used to create the data sets contain an
error.  For full transparency, we've released the scripts used to collect the
data set at (This will be added after the anonymous review).

@@

\noindent\textbf{External validity:} 
While we have used a data set with high quality standards~\cite{msr17challenge},
these results may not generalized to non-open source projects.

\noindent\textbf{Construct validity:}
While we believe the build status is a good metric for contribution success,
there is the chance that a problem in the projects's test cases, and no the
contribution itself, led to the build failure.

\section{Conclusion}
In this study we have analyzed the ability to use social factors to predict
build integration success.
Our results show that adding social data, which proxies experience, provides a
small increases in prediction accuracy.  This leads us to conclude that while
experience is important, it is not the only factor in build success.
We have also found that non-core contributors cause not successful builds more
than core contributors.  This leads us to believe that non-core contributions
are not inspected as closely as they should be.

>>>>

We evaluated the predictive power of the social factors using a decision
tree~\cite{Quinlan86}.
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the Weka~\cite{Weka} J48~\cite{Quinlan1993} decision tree
with default settings. The decision trees were evaluated using ten fold cross 
validation with the data in each data set.

@@

\subsection{Follower effect on build success}

We also investigated if developers with followers were more likely to have a
successful build integration, since have followers may be seen as vouching for
the developer's abilities.  We specifically investigated if a developer with 
followers was more likely to pass the build.  We found that only 0.87\% of the
contributions in the data set was performed by developers with zero 
followers (excluding the developers in which we were not able to extract profile
information for). We found that 99.13\% of the contributions were performed by
developers with at least one or more followers.
We found that developers with 0 followers had a successful build commit 68.49\%
of the time.  Developers with one or more followers were successful 74.78\% of
the time.

We also investigated developers with a large number of followers (1000 or more
followers).  We found that 6.94\% of the contributions in the data set were
performed by developers with 1000 or more followers.  We found that these
contributions had a 78.61\% success rate.

@@

The follower results indicate that developers with more followers are more
likely to pass the build, although followers are not a perfect indicator.
Developers with over 1000 followers had more than a 10\% increase compared to
developers with no followers.  This shows that high-quality developers are more
likely to have a large number of followers.

@@

\noindent\textbf{Internal validity:}\\
One source of internal validity concern is the time mismatch between the
technical and social data.  We restricted the commits to only the commits in the
last three years of the data set to reduce this concern.
There is also a chance that scripts we used to create the data sets contain an
error.  For full transparency, we've released the scripts used to collect the
data set at (This will be added after the anonymous review).

@@

\noindent\textbf{External validity:} \\
While we have used a data set with high quality standards~\cite{msr17challenge},
these results may not generalized to non-open source projects.

\noindent\textbf{Construct validity:}\\
While we believe the build status is a good metric for contribution success,
there is the chance that a problem in the project's test cases, and not the
contribution itself, led to the build failure.  There are also other possible
technical and social factors which were not explored in this study.  Future
research will be required to determine if those factors are important.

\section{Conclusion}
In this study we have analyzed the ability to use social factors to predict
build integration success.
Our results show that adding social data, which proxies experience, provides a
small increases in prediction accuracy.  This leads us to conclude that while
experience is important, it is not the only factor in build success.
We have also found that non-core contributors cause not successful builds more
than core contributors.  This leads us to believe that non-core contributions
are not inspected as closely as they should be.  We have also found that having
a follower, and especially a large follower base, can be an indicator of build
integration success.
